### 2016-07-15 testbed_http.tex
Few changes

At the end of Section~\ref{sec:overlay_fs}, the final customized image was
proposed to be splitted into three partitions. One for the boot files, one
containing the root file system and one for the home directory. This is made
considering an overlay filesystem approach. In this section, instead of
writing the image direclty to the memory cards, we present how the
partitions can be extracted from the image, and how the boot partition can
be configured to download the root filesystem and home directory partitions
from a \ac{HTTP} server during startup. The advantage of this setup is that
we completely automate the image fetch which significantly eases its
maintainance since any changes are required to be made only in the \ac{HTTP}
server image. We start by declaring the variables for the path names of each
partition:

>>>>

At the end of Section~\ref{sec:overlay_fs}, the final customized image was
proposed to be splitted into three partitions. One for the boot files, one
containing the root file system and one for the home directory. This is made
considering an overlay filesystem approach. In this section, instead of
working with three partitions and writing the image directly to the memory
cards, we present how to configure the boot partition to download the root
filesystem partition and also configure the home directory partitions
from a \ac{HTTP} server during startup. The advantage of this setup is that
we completely automate the image fetch which significantly eases its
maintainance since any changes are required to be made only in the \ac{HTTP}
server image. We start by declaring the variables for the path names of each
partition:
